Summary

### 2015-10-30 inst/examples/summary.Rmd
ok

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)

[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_conversion.csv)

>>>>

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv) (Check that ok to discard these)

[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv) (Check for formatting and synonymes)
